### 2020-06-25 README.Rmd
Fixed README to account for diff notion of species

```{r, eval = FALSE}
# Number of permutation shuffles:
num_shuffle <- 4

# Compute observed RMSE for all models, but only do permutation shuffling for
# models 3,6,9
model_numbers <- c(3)

# Save results here
run_time <- rep(0, length(model_numbers))
observed_RMSE <- rep(0, length(model_numbers))
observed_RMSE_CV <- rep(0, length(model_numbers))
shuffle_RMSE <- list()
shuffle_RMSE_CV <- list()

for(i in 1:length(model_numbers)){
  # Start clock
  tic()

  # Modeling and species stuff
  model_number <- model_numbers[i]
  bw_specs <- bw_growth_df %>% 
    get_model_specs(model_number = model_number, species_notion = 'trait_group')

@@

      # Status update
      str_c("Model ", model_numbers[i], ", shuffle with permutation ", j) %>% print()
    }
  } else {
    shuffle_RMSE_CV[[i]] <- NA
  }

>>>>

```{r, eval = FALSE}
# Number of permutation shuffles:
num_shuffle <- 2

# Compute observed RMSE for all models, but only do permutation shuffling for
# models 3,6,9
model_numbers <- c(3)
species_notion_vector <- c("trait_group", "family", "species")

# Save results here
run_time <- rep(0, length(species_notion_vector))
observed_RMSE <- rep(0, length(species_notion_vector))
observed_RMSE_CV <- rep(0, length(species_notion_vector))
shuffle_RMSE <- list()
shuffle_RMSE_CV <- list()

for(i in 1:length(species_notion_vector)){
  # Start clock
  tic()

  # Modeling and species stuff
  model_number <- 3
  species_notion <- species_notion_vector[i]
  bw_specs <- bw_growth_df %>% 
    get_model_specs(model_number = model_number, species_notion = species_notion)

@@

      # Status update
      str_c("notion of species: ", species_notion_vector[i], ", shuffle with permutation ", j) %>% print()
    }
  } else {
    shuffle_RMSE_CV[[i]] <- NA
  }
